Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-27 ITiCSE2019.tex
Txt around vulnerabilities

\subsection{The case of Java}\label{sec:Java}
To the best of the authors' knowledge, no survey equivalent to \cite{Drop2019} has been done for Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resuorces. \cite{Mengetal2018a} analysed 503 Cybersecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implcitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling they check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''. As of writing (16 January 2018) there were no negative comments about this disabling of a vital security feature.

\cite{Chenetal2019a,Zorz2019a,Fischeretal2017a}

\subsection{Staff}
It is well known that Cybersecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
\begin{quote}

\end{quote}
JHD possibly to write about his recruitment experiences.  ? more IoC input?

>>>>

\subsection{The case of Java}\label{sec:Java}
To the best of the authors' knowledge, no survey equivalent to \cite{Drop2019} has been done for Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resources. \cite{Mengetal2018a} analysed 503 Cybersecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implcitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling they check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''. As of writing (16 January 2018) there were no negative comments about this disabling of a vital security feature.
\par
\cite{Chenetal2019a,Zorz2019a} 
\subsection{Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.

\subsection{Staff}
It is well known that Cybersecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
The ESG survey is international, but ESG have confirmed that the UK figures are very similar.
%JHD possibly to write about his recruitment experiences.  ? more IoC input?
